---
title: 'Scatter Plots '
author: Ella DiPietro
date: '2017-09-28'
slug: scatter-plots
categories: []
tags:
  - Data Visualization
  - Scatter Plots
---

For our first post, we will create scatter plots using information from the Lahman's Baseball database. First, we will need to download some packages and bring them in:

```{r, message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)

```

Now, we can use these tools to find the homerun and strikout totals for players who have hit more than 400 homeruns. We will store the result of our query for use later:

```{r}
query<-"SELECT playerID,sum(HR) AS career_HR,sum(SO) AS career_SO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>=400"

sqldf(query)
result<-sqldf(query)
```

Now, we can visualize the data in a scatter plot. The top left corner has the players with the most homeruns and the least strikeouts:

```{r, message=FALSE, warning=FALSE}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR))
```

We can customize the table by adding a title, changing the name of the x and y axis, and making the points larger and blue:

```{r, message=FALSE, warning=FALSE}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR),size=3,color="blue")+
  ggtitle("Career Strikeouts and Homeruns for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```

