---
title: Time Series
author: 'Ella DiPietro '
date: '2017-10-02'
slug: time-series
categories: []
tags:
  - Data Visualization
  - Time Series
---

We can use a time series graph to show how data changes over time. For this visualization we will need the same tools that we used before. Let's bring them in with library:

```{r, message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```


Now, lets make a query to find Babe Ruth homerun totals over the course of his career. We can save the result of the query to make our time series graph:

```{r}
query<-"Select yearID, HR From Batting
where playerID='ruthba01'"
sqldf(query)
result<-sqldf(query)
```

We can use ggplot again to make the time series graph with this information. We can add points and connect them with lines to show progress over time:

```{r}
ggplot()+
  geom_point(data=result, aes(x=yearID, y=HR), size=2.5)+
  geom_line(data=result, aes(x=yearID, y=HR))+
  ggtitle("Babe Ruth's Homeruns Throughout his Career")
```

Looks great! What a guy. 