---
title: 'Histograms '
author: Ella DiPietro
date: '2017-09-30'
slug: histograms
categories: []
tags:
  - Data Visualization
  - Histograms
---

Here's another way to visualize data from the Lahmans Baseball Data Base. Again, we'll need to bring in the tools with library:

```{r, message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

We want to see the weight distribution of baseball players, so let's pull that data from Lahman's Master Table and store the result of the query for later use:

query<-"SELECT weight FROM Master"
sqldf(query)
result<-sqldf(query)

```{r, message=FALSE, warning=FALSE, include=FALSE}
query<-"SELECT weight FROM Master"
sqldf(query)
result<-sqldf(query)
```


Now, lets visualize the distibution in a Histogram. We'll use ggplot again for this:

```{r, message=FALSE, warning=FALSE}
ggplot()+
  geom_histogram(data=result,aes(x=weight))
```

Now, we can manipulate the command to make the Histogram more visually appealing. Lets try changing the color, fill, and number of bins. We can also add a title:

```{r, message=FALSE, warning=FALSE}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="white",bins=60)+
  ggtitle("Weight Distibution of Baseball Players")
  
```

